Heuristics and Really Hard Instances for Subgraph Isomorphism Problems

### 2016-01-11 paper/paper.tex
Muck around a bit

% \usepackage{showframe}

@@

\begin{figure*}[tb]
    \input{gen-graph-induced.tex}
    \caption{Behaviour of algorithms on the induced variant, shown in the style
    of \cref{figure:non-induced}. The second row shows a bound on the satisfiable region, by
    considering where a \emph{non-}induced isomorphism may also be a non-induced isomorphism between
    complement graphs.}\label{figure:induced}
\end{figure*}

@@

\begin{figure*}[t]
    \input{gen-graph-sat.tex}
    \caption{Behaviour of other solvers on the induced variant on smaller graphs, shown in the style of
        \cref{figure:non-induced}. The second row shows the number of search nodes used by the Glasgow
        algorithm, the third row shows the number of decisions made by the Clasp pseudo-boolean solver,
        the fourth row shows the number of search nodes used by a clique encoding, and the fifth a mixed
        integer encoding with Gurobi.}\label{figure:alt}
\end{figure*}

@@

Clique encoding: association graph, a version of BBMC modified to solve the decision problem. The
hard instances in the central region remain hard. Additionally, some of the easy satisfiable
instances become hard. Possible weakness of clique algorithms for this kind of input.

MIP encoding with Gurobi.

@@

?? \citep{Lipets:2009}

@@

>>>>

\usepackage{showframe}

@@

\begin{figure*}[p]
    \input{gen-graph-induced.tex}
    \caption{Behaviour of algorithms on the induced variant, shown in the style
    of \cref{figure:non-induced}. The second row shows a bound on the satisfiable region, by
    considering where a \emph{non-}induced isomorphism may also be a non-induced isomorphism between
    complement graphs.}\label{figure:induced}
\end{figure*}

@@

\begin{figure*}[t]
    \input{gen-graph-sat.tex}
    \caption{Behaviour of other solvers on the induced variant on smaller graphs, shown in the style of
        \cref{figure:non-induced}. The second row shows the number of search nodes used by the
    Glasgow algorithm, the third row shows the number of decisions made by the Clasp pseudo-boolean
solver, and the fourth row shows the number of search nodes used by a clique
encoding.}\label{figure:alt}
\end{figure*}

@@

We also tried using a mixed integer encoding along similar lines. Gurobi was only able to solve some
of the trivial satisfiable instances, and was almost never able to prove unsatisfiability within the
time limit. We do not plot these results.

Clique encoding: association graph, a version of BBMC modified to solve the decision problem. The
hard instances in the central region remain hard. Additionally, some of the easy satisfiable
instances become hard. Possible weakness in variable ordering heuristics.

Some easy instances become hard, here, but hard instances remain hard. In particular, the large
central region for the larger pattern graphs which is not near the phase transitions is still
relatively difficult in all encodings. This suggests that these instances may genuinely be hard,
despite not being near a phase transition, and that this does not indicate a weakness in subgraph
isomorphism solvers.

@@

@@

?? \citep{Lipets:2009} inexact solutions?
